\chapter{Objectives}

\paragraph*{}
Many physical feats to automate daily tasks are only available using robotic solutions. However, a single complex robot is not viable in every scenario due to its limited reach and high spatial and monetary investment. Thus, we turn to a simpler, more scalable solution, which is swarm robotics. Our objective is to have 3 decentralised robots working together to achieve a goal, more specifically collective transportation of an object for cleaning/tidying up a room. This requires robustness in localisation and awareness of other robots' movements.

\paragraph*{}
Given the time constraints, creating a finished fleet of cleaning robots would be unrealistic. The project is then scaled down and split into 2 major milestones: localisation with object identification, and object grasping through coordinated formations. The first milestone is crucial as it provides a functional component relevant to domestic use cases, enabling object identification, localization, and communication, all of which are key to managing a scalable fleet. Secondly, object grasping through coordinated formations is a crucial follow-up as it expands further upon an abstract concept to pinpoint specific use cases such as tidying items in a room. Last semester, we successfully developed a minimal viable prototype within a simulation environment. This semester, we aim to transition our simulation-based prototype into a real-world implementation. However, simulation will continue to play a key role, particularly for testing and validating graph SLAM methodologies.

