\chapter{Project Contribution per Student}

\paragraph*{}
In the first phase, from January to early March of the second semester, the focus is on more advanced capabilities from a practical standpoint, including communication in the swarm, more specifically, between the Jetsons. Two group members will work on this task with the ideal target being communication between three members of the swarm over Wifi. Alongside, Simultaneous Localization and Mapping in the Simulation will also be developed, with the task being allocated to two group members. The goal for these tasks is to allow the robots to adapt to the infinite possibilities of the environment, as well as coordinate to eliminate redundancies in the swarm's intended functionalities, such as in repeated mapping scenarios.

\paragraph*{}
The first phase also includes gripping mechanisms and coordinated movement. Three group members will work on the coordinated gripping task, preparing the static gripper for future sliding movements, as well as developing strategies for a robust robot path planning algorithm. Meanwhile, another two members will integrate camera with Lidar in order to perform object detection, as well as implement pose estimation for object detection of varying targets

\paragraph*{}
The second phase, ranging from February to early May, includes moving towards a complete swarm system, with the prerequisites being hardware, movement after gripping, and testing and evaluation. We consider hardware to be one major overhead, which we have to continuously work on; thus, it will be collaboratively completed by all our group members. Together with this, methods towards collective movement together with the gripped object will be considered by three group members. Our group plans to have this completed by the middle of April, to allocate some time for further testing and evaluation that can help us towards a more complete version of the swarm system, or identify potential flaws for future references. Testing and Evaluation will also be done by all our group members starting from the middle of May.
